### 2016-10-01 results.tex
cheers

Looking ahead to the next section, we will analyze a closely related construction, which was attacked by Niedermeyer et al.~\cite{niedermeyer2014cryptanalysis} in the context of private medical-record linkage.  It uses the same linear-PRF hash functions, but has a $\Rep$ algorithm that that does not ensure that the hash functions are called on \emph{distinct} values.  We show that this is \emph{not} private with respect to our SS notion for a leakage function that leaks nearly the entire set~$S$. \todo{It would be better, perhaps, to show that it is not OW secure, since this implies it isn't SS secure, and OW security is what Niedermeyer et al. violate.}

>>>>

Looking ahead to the next section, we will analyze a closely related
construction, which was attacked by Niedermeyer et
al.~\cite{niedermeyer2014cryptanalysis} in the context of private
medical-record linkage.  It uses the same linear-PRF hash functions,
but has a $\Rep$ algorithm that that does not ensure that the hash
functions are called on \emph{distinct} values.  We show that this is
\emph{not} private with respect to our SS notion for a leakage
function that leaks nearly the entire set~$S$. 
%\todo{It would be better, perhaps, to show that it is not OW secure, since this implies it isn't SS secure, and OW security is what Niedermeyer et al. violate.}
